---
title: "Advanced Features"
author: "Marcus Young, modified by Malcolm Morganr"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Introduction

The vignette introduces some of the more advanced features of OTP, and gives some examples of the types of anlaysis that are possible when using OTP and R togther.

### Recap

For this vingnette we will use the same data as the `getting_started` vingette. If you have not yet created the example graph you can set it up with the following commands. If you are using non-default settings see the `getting_started` vingette for full details.

```{r eval = FALSE}
library(opentripplanner)
# Path to a folder containing the OTP.jar file, change to where you saved the file.
path_otp <- "C:/otp"

path_data <- system.file("extdata", package="opentripplanner")
log <- otp_build_graph(otp = path_otp, dir = path_data)
otp_setup(otp = path_otp, dir = path_data, memory = 1.5)
otpcon <- otp_connect()

```

## Isochrones

Now that we have a working instance of OTP, we'll use it to generate some travel-time isochrones. We are interested in visualising how long it takes to access Manchester Airport using public transport from different parts of Greater Manchester. We will do this by requesting isochrones from OTP for 15, 30, 45, 60, 75 and 90 minutes. This can be achieved with a single function `otp_isochrone()`.

```{r eval = FALSE}
airport_current  <- otp_isochrone(otpcon = otpcon,
            fromPlace = c(53.3627432, -2.2729342), # latlong of Manchester Airport
            cutoffSec = c(15, 30, 45, 60, 75, 90) * 60 )# Cut offs in seconds

```

We can visualise the isochrones on a map using the `tmap` package.

```{r, eval = FALSE}
library(tmap)                       # Load the tmap package
tmap_mode("view")                   # Set tmap to interative viewing
qtm(airport_current, fill = "time") # Plot the route on a map
```
